A few stickleback suffice to transport adaptive alleles to new lakes

### 2018-12-08 Stickleback_Paper.tex
.

\paragraph{Recording genealogical history}
We used SLiM's ability to record \emph{tree sequences} \citep{haller2018treeseq}
to record the genealogical history of all individuals alive 
at the time of introduction of new lakes, the time of adaptation, and the end of the simulation.
This allowed us to directly query the true origins of adaptive alleles,
as well as allowing much larger simulations
by avoiding the computationally expensive task of simulating neutral mutations
(which were added after the fact at a rate of $10^{-7}$ per locus per generation, 
as described in \citet{kelleher2018efficient}).

>>>>

\paragraph{Recording genealogical history}
We used SLiM's ability to record \emph{tree sequences} \citep{haller2018treesequence}
to record the genealogical history of all individuals alive 
at the time of introduction of new lakes, the time of adaptation, and the end of the simulation.
This allowed us to directly query the true origins of adaptive alleles,
as well as allowing much larger simulations
by avoiding the computationally expensive task of simulating neutral mutations
(which were added after the fact at a rate of $10^{-7}$ per locus per generation, 
as described in \citet{kelleher2018efficient}).
